The Hydrogen Epoch of Reionization Array Dish I: Beam Pattern Measurements and Science Implications

### 2016-12-07 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev4_submitted.tex
update to published version

\author{Abraham R. Neben\altaffilmark{1,2},
Richard F. Bradley\altaffilmark{3,4},
Jacqueline N. Hewitt\altaffilmark{1,2},
David R. DeBoer\altaffilmark{5},
Aaron R. Parsons\altaffilmark{5},
James E. Aguirre\altaffilmark{7},
Zaki S. Ali\altaffilmark{5},
Carina Cheng\altaffilmark{5},
Aaron Ewall-Wice\altaffilmark{1,2},
Nipanjana Patra\altaffilmark{5},
Nithyanandan Thyagarajan\altaffilmark{6},
Judd Bowman\altaffilmark{6},
Roger Dickenson\altaffilmark{4},
Joshua S. Dillon\altaffilmark{5},
Phillip Doolittle\altaffilmark{4},
Dennis Egan\altaffilmark{4},
Mike Hedrick\altaffilmark{4},
Daniel C. Jacobs\altaffilmark{6},
Saul A. Kohn\altaffilmark{7},
Patricia J. Klima\altaffilmark{4},
Kavilan Moodley\altaffilmark{8},
Benjamin R.B. Saliwanchik\altaffilmark{8},
Patrick Schaffner\altaffilmark{4},
John Shelton\altaffilmark{4},
H.A. Taylor\altaffilmark{4},
Rusty Taylor\altaffilmark{4},
Butch Wirt\altaffilmark{4},
Haoxuan Zheng\altaffilmark{1,2}}

@@

In detail, we simulate visibilities using PRISim\footnote{https://github.com/nithyanandan/PRISim} for each beam model at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and the NVSS \citep{nvss} and SUMSS \citep{sumss,sumss2} point source catalogs. We use a frequency spacing of 781\,kHz, sufficient to characterize delays within and just outside of the horizon limits on both baseline lengths considered, 14.6\,m and 43.8\,m. We use a total bandwidth of 100\,MHz (effectively reduced to 50\,MHz after applying the Blackman-Harris window) centered on 150\,MHz. This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution with redshift, but is the bandwidth used in the wide band delay space foreground filter of \citet{paper32,ali2015}.

>>>>

\author{Abraham R. Neben\altaffilmark{1,2},
Richard F. Bradley\altaffilmark{3,4},
Jacqueline N. Hewitt\altaffilmark{1,2},
David R. DeBoer\altaffilmark{5},
Aaron R. Parsons\altaffilmark{5},
James E. Aguirre\altaffilmark{7},
Zaki S. Ali\altaffilmark{5},
Carina Cheng\altaffilmark{5},
Aaron Ewall-Wice\altaffilmark{1,2},
Nipanjana Patra\altaffilmark{5},
Nithyanandan Thyagarajan\altaffilmark{6},
Judd Bowman\altaffilmark{6},
Roger Dickenson\altaffilmark{4},
Joshua S. Dillon\altaffilmark{5},
Phillip Doolittle\altaffilmark{4},
Dennis Egan\altaffilmark{4},
Mike Hedrick\altaffilmark{4},
Daniel C. Jacobs\altaffilmark{6},
Saul A. Kohn\altaffilmark{7},
Patricia J. Klima\altaffilmark{4},
Kavilan Moodley\altaffilmark{8},
Benjamin R.B. Saliwanchik\altaffilmark{8},
Patrick Schaffner\altaffilmark{4},
John Shelton\altaffilmark{4},
H.A. Taylor\altaffilmark{4},
Rusty Taylor\altaffilmark{4},
Max Tegmark\altaffilmark{1,2},
Butch Wirt\altaffilmark{4},
Haoxuan Zheng\altaffilmark{1,2}}

@@

In detail, we simulate visibilities using the Precision Radio Interferometry Simulator\footnote{https://github.com/nithyanandan/PRISim} (PRISim) for each beam model at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and the NVSS \citep{nvss} and SUMSS \citep{sumss,sumss2} point source catalogs. We use a frequency spacing of 781\,kHz, sufficient to characterize delays within and just outside of the horizon limits on both baseline lengths considered, 14.6\,m and 43.8\,m. We use a total bandwidth of 100\,MHz (effectively reduced to 50\,MHz after applying the Blackman-Harris window) centered on 150\,MHz. This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution with redshift, but is the bandwidth used in the wide band delay space foreground filter of \citet{paper32,ali2015}.
